---
title: "ARCH-vue Dashboard"
# author: "Hossein Estiri"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    social: menu
    # source_code: embed
    # vertical_layout: scroll
runtime: shiny
---

```{r setup, include=FALSE}
options(scipen = 999)
if (!require("easypackages")) install.packages('easypackages', repos = "http://cran.rstudio.com/")

packages("data.table","devtools","dplyr","DT","ggplot2","gridExtra","htmlwidgets","knitr",
         "rmarkdown","plotly","treemap","reshape2","visNetwork","rmdformats","ggrepel",
         "flexdashboard","highcharter","viridisLite","shiny","DiagrammeR","collapsibleTree","lubridate",
         prompt = F)

if (names(dev.cur()) != "null device") dev.off()
pdf(NULL)

Net.Name = "NetworkName" 

### data model
data.model = "PCORnet v.3" 
cdm = "PCORNET3"


# primary key for population count
pop.key = "patid"

# source("id.R")
percent = function(x, digits = 2, format = "f", ...) {
  paste0(formatC(x*100, format = format, digits = digits, ...), "%")
}

source(paste0(getwd(),"/collapsibleTreeShiny.R"))
source(paste0(getwd(),"/collapsibleTreeSummary.R"))


pth = paste0(getwd(),"/site.reports") #set the path to where DQe-c report files from individual sites are stored
report.tables = data.frame(table.names=list.files(pth))
report.tables$table.group = substr(report.tables$table.names, 0,7)
for (i in 1:length(report.tables$table.names)) {
report.tables$date[i] = as.character(substr(report.tables$table.names[i], 
                                nchar(as.character(report.tables$table.names[i]))-13,
                                nchar(as.character(report.tables$table.names[i]))-4))
if (report.tables$table.group[i] == "without") {
report.tables$organization[i] = as.character(substr(report.tables$table.names[i], 
                                9+nchar(cdm)+2,
                                nchar(as.character(report.tables$table.names[i]))-15))
} else if (report.tables$table.group[i] == "DQ_Mast") {
  report.tables$organization[i] = as.character(substr(report.tables$table.names[i], 
                                16+nchar(cdm)+2,
                                nchar(as.character(report.tables$table.names[i]))-15))
}
}
report.tables$date <- dmy(report.tables$date)


##obtaining the latest test dates available by site and group
latests.test.dates = aggregate(report.tables$date, by = list(report.tables$organization,report.tables$table.group), max)
colnames(latests.test.dates) = c("site", "table.group","date")

rounds <- list()
for (i in 1:length(unique(report.tables$organization))) {
  org <- unique(report.tables$organization)[i]
  sub.tab <- data.frame(unique(subset(report.tables$date, 
                                     report.tables$organization == org)))
  colnames(sub.tab) <- "test_date"
  sub.tab$organization <- org
  sub.tab <- data.frame(sub.tab[order(sub.tab$test_date,decreasing = F),])
  sub.tab$round <- seq.int(nrow(sub.tab))
  rounds[[i]] <- sub.tab
}

DQ.rounds <- do.call(rbind, lapply(rounds, data.frame, stringsAsFactors=FALSE))


# extracting DQ_Master tables
DQ_Master.names <- report.tables[(report.tables$table.group == "DQ_Mast"),"table.names"]
# reading in all DQ_Master tables
ms.tables <- list()
for (l in 1:length(DQ_Master.names)) {
  ms.tables[[l]] <- data.frame(read.csv(paste0(pth,"/",DQ_Master.names[l])))
}
DQ.Master <- do.call(rbind, lapply(ms.tables, data.frame, stringsAsFactors=FALSE))
rm(ms.tables)


# DQ.Master$test_date <- as.Date(DQ.Master$test_date, format = "%m-%d-%Y")
DQ.Master$test_date <- mdy(DQ.Master$test_date) 
DQ.Master <- merge(DQ.Master,DQ.rounds, by=c("organization","test_date"), all.x = TRUE)

latest.DQM <- aggregate(DQ.Master$test_date, by = list(DQ.Master$organization), max)
latest.DQM$run.char <- paste0(latest.DQM$Group.1,latest.DQM$x)

latest.DQM.round <- aggregate(DQ.Master$round, by = list(DQ.Master$organization), max)
latest.DQM.round$round.char <- paste0(latest.DQM.round$Group.1,latest.DQM.round$x)



DQ.Master$run.char <- paste0(DQ.Master$organization,DQ.Master$test_date)
DQ.Master$round.char <- paste0(DQ.Master$organization,DQ.Master$round)



# subseting the latest DQ.Master
DQ.Master.latest <- select(subset(DQ.Master,DQ.Master$run.char %in% c(latest.DQM$run.char)), TabNam,ColNam,test_date,FRQ,UNIQFRQ,MS1_FRQ,MS2_FRQ,MSs_PERC,organization,round, DQLVL)


###with
without.names <- report.tables[(report.tables$table.group == "without"),"table.names"]
without.tabs <- list()
for (w in 1:length(without.names)) {
  without.tabs[[w]] <- data.frame(read.csv(paste0(pth,"/",without.names[w])))
}

withouts.network <- do.call(rbind, lapply(without.tabs, data.frame, stringsAsFactors=FALSE))
rm(without.tabs)


withouts.network$missing.population <- round((withouts.network$missing.percentage/100)*withouts.network$denominator,0)

withouts.network$missing.ratio <- withouts.network$missing.percentage/100


withouts.network$test_date <- mdy(withouts.network$test_date) 
# withouts.network$test_date = as.Date(withouts.network$test_date, format = "%m-%d-%Y")

withouts.network <- merge(withouts.network,DQ.rounds, by=c("organization","test_date"), all.x = TRUE)

latest.withouts.network <- aggregate(withouts.network$test_date, by = list(withouts.network$organization), max)
latest.withouts.network$run.char <- paste0(latest.withouts.network$Group.1,latest.withouts.network$x)
withouts.network$round.x <- withouts.network$round
latest.withouts.network.round <- aggregate(withouts.network$round, by = list(withouts.network$organization), max)
latest.withouts.network.round$round.char <- paste0(latest.withouts.network.round$Group.1,latest.withouts.network.round$x)

withouts.network$run.char <- paste0(withouts.network$organization,withouts.network$test_date)
withouts.network$round.char <- paste0(withouts.network$organization,withouts.network$round)

# subseting the latest withouts table
withouts.network.latest <- select(subset(withouts.network,withouts.network$run.char %in% c(latest.withouts.network$run.char)),group,missing.percentage,missing.population,denominator,perc,organization,test_date, missing.ratio)
                                 
# 
withouts.network.latest.aggregate <- withouts.network.latest %>% group_by(group) %>% summarise(missing.pop = sum(missing.population),denominator = sum(denominator))

# 
withouts.network.latest.aggregate$missing.ratio <- round((withouts.network.latest.aggregate$missing.pop/withouts.network.latest.aggregate$denominator),4)
withouts.network.latest.aggregate$perc <- percent(withouts.network.latest.aggregate$missing.ratio)
withouts.network.latest.aggregate$organization <- "Network"
withouts.network.latest.aggregate$test_date <- as.character(format(Sys.Date(),"%m-%d-%Y"))


############# population projections

pops <- select(subset(DQ.Master, DQ.Master$TabNam == "demographic" & DQ.Master$ColNam == "patid"),organization,test_date,UNIQFRQ,round,run.char,round.char)
pops$difftime <- 9999
min.run <- min(pops$test_date)
pops$difftime <- ifelse(pops$test_date == min.run, 
                       0.1,
                        pops$difftime)

##calculating time difference in days from first ime
pops$difftime.orig <- ifelse(pops$test_date == min.run, 
                             0.1,
                             as.numeric(difftime(pops$test_date,
                                          min.run, tz="",units = c("days"))))


##calculating time difference in days from the previous time
for (i in 2:nrow(pops)) {
  pops[order(as.Date(pops$test_date)),7][i] <- as.numeric(difftime(pops[order(as.Date(pops$test_date)),2][i],
                                                                   pops[order(as.Date(pops$test_date)),2][i-1], tz="",units = c("days")))
  
  
}



setDT(pops)
pops.wide <- dcast(pops, test_date +difftime.orig ~ organization, value.var="UNIQFRQ", fun.aggregate = sum)
pops.wide[pops.wide == 0] <- NA

pops.proj <- list()
resids <- data.frame(cbind(degree=c(1,2,3,4,5),
                     residual = c(0,0,0,0,0)))
for (j in 3:dim(pops.wide)[2]){
  oo <- pops.wide[,c(1,2,j)]
  name <- colnames(oo)[3]
  colnames(oo)[3] <- "UNIQFRQ"
  oo$organization <- name
  train <- subset(oo,!is.na(oo$UNIQFRQ))
  oo$projection <- ifelse(!is.na(oo$UNIQFRQ), "observed", "estimate")
  
        # finding the min residual model
        for (d in 1:nrow(resids)){
        fit.test <- lm(UNIQFRQ~poly(difftime.orig, d, raw=T),data=train)
        resids[resids$degree == d,2] <- as.numeric(predict(fit.test,newdata=oo,interval="confidence",
                level = 0.95,type="response",se = TRUE)$residual.scale)
        }
  r2 <- subset(resids,!is.na(resids$residual))
  min.res <- ifelse(min((r2$residual)) == 0 ,1,min(r2$residual))
  best.dg <- as.numeric(r2[r2$residual == min.res,1])
  resids$residual <- 0
  fit <- lm(UNIQFRQ~poly(difftime.orig, best.dg, raw=T),data=train)
  oo$pred.UNIQFRQ <- predict(fit,newdata=oo,interval="confidence",
                                 level = 0.95,type="response",se = TRUE)$fit[,1]
  oo$pred.low.UNIQFRQ <- predict(fit,newdata=oo,interval="confidence",
                                        level = 0.95,type="response",se = TRUE)$fit[,2]
  oo$pred.high.UNIQFRQ <- predict(fit,newdata=oo,interval="confidence",
                                        level = 0.95,type="response",se = TRUE)$fit[,3]
  oo$pred.UNIQFRQ <- ifelse(!is.na(oo$UNIQFRQ), oo$UNIQFRQ, oo$pred.UNIQFRQ)
  oo$pred.low.UNIQFRQ <- ifelse(!is.na(oo$UNIQFRQ), 0, oo$pred.low.UNIQFRQ)
  oo$pred.high.UNIQFRQ <- ifelse(!is.na(oo$UNIQFRQ), 0, oo$pred.high.UNIQFRQ)
  oo$ci <- ifelse(!is.na(oo$UNIQFRQ), 0, oo$pred.UNIQFRQ-oo$pred.low.UNIQFRQ)
  
  oo$best.dg <- best.dg
  rm(fit)
  
  pops.proj[[j]] <- oo
  rm(oo)
  
}

comp.pop <- do.call(rbind, lapply(pops.proj, data.frame, stringsAsFactors=FALSE))
rm(pops)
# comp.pop.agg <- dcast(comp.pop, test_date ~ , value.var="UNIQFRQ", fun.aggregate = sum)
comp.pop.agg <-aggregate(list(pred.UNIQFRQ=comp.pop$pred.UNIQFRQ,pred.low.UNIQFRQ=comp.pop$pred.low.UNIQFRQ,pred.high.UNIQFRQ=comp.pop$pred.high.UNIQFRQ), by = list(test_date=comp.pop$test_date), sum)
comp.pop.agg$difftime.orig <- 999
comp.pop.agg$UNIQFRQ <- 999
comp.pop.agg$organization <- "NETWORK NAME"
comp.pop.agg$projection <- "estimate"
comp.pop.agg$best.dg <- 9999
comp.pop.agg.ci <-aggregate(list(ci=comp.pop$ci), by = list(test_date=comp.pop$test_date), mean)
comp.pop.agg <- merge(comp.pop.agg,comp.pop.agg.ci,by="test_date")
comp.pop <- rbind(comp.pop,comp.pop.agg)
comp.pop$pred.low.UNIQFRQ <- comp.pop$pred.UNIQFRQ-comp.pop$ci
comp.pop$pred.high.UNIQFRQ <- comp.pop$pred.UNIQFRQ+comp.pop$ci


```



Selections {.sidebar}
===============================

###Select Network Site
Dashboard has data from **`r length(unique(DQ.Master$organization))`** **`r Net.Name`** Network participating sites. 


```{r}
## The shiny part
selectInput("site", label = "Network site", 
            c("Network","site 1","site 2","site n"))


```



Preview
=======================================================================

Row
-----------------------------------------------------------------------

### Total Network Unique Patients {.value-box}

```{r}

# Emit the user count
renderValueBox({
  valueBox(value = format(sum(subset(DQ.Master.latest$UNIQFRQ, (DQ.Master.latest$TabNam == "demographic" & DQ.Master.latest$ColNam == "patid"))),big.mark=",", trim=TRUE), icon = "fa-users")
})
```

### Total Network Unique Encounters {.value-box}

```{r}

# Emit the user count
renderValueBox({
  valueBox(value = format(sum(subset(DQ.Master.latest$UNIQFRQ, (DQ.Master.latest$TabNam == "encounter" & DQ.Master.latest$ColNam == "encounterid"))),big.mark=",", trim=TRUE), icon = "fa-area-chart")
})

```

### Total Network Unique Diagnosis IDs {.value-box}

```{r}

# Emit the user count
renderValueBox({
  valueBox(value = format(sum(subset(DQ.Master.latest$UNIQFRQ, (DQ.Master.latest$TabNam == "procedures" & DQ.Master.latest$ColNam == "proceduresid"))),big.mark=",", trim=TRUE), 
           icon = "fa-file-text")
})
```


Row
-----------------------------------------------------------------------
### Total Site Unique Patients {.value-box}
```{r}

  renderValueBox({
  valueBox(value = if (input$site != "Network") format(sum(DQ.Master.latest[(DQ.Master.latest$TabNam == "demographic" & DQ.Master.latest$ColNam == "patid" & DQ.Master.latest$organization==input$site),"UNIQFRQ"]),big.mark=",", trim=TRUE), 
           icon = if (input$site != "Network") "fa-users", color = "orange")
})

```

### Total Site Unique Encounters {.value-box}
```{r}

renderValueBox({
  valueBox(value = if (input$site != "Network") format(sum(DQ.Master.latest[(DQ.Master.latest$TabNam == "encounter" & DQ.Master.latest$ColNam == "encounterid" & DQ.Master.latest$organization==input$site),"UNIQFRQ"]),big.mark=",", trim=TRUE), 
           icon = if (input$site != "Network") "fa-area-chart", color = "orange")
})
```


### Total Site Unique Diagnosis IDs {.value-box}

```{r}

renderValueBox({
  valueBox(value = if (input$site != "Network") format(sum(DQ.Master.latest[(DQ.Master.latest$TabNam == "procedures" & DQ.Master.latest$ColNam == "proceduresid" & DQ.Master.latest$organization==input$site),"UNIQFRQ"]),big.mark=",", trim=TRUE), 
           icon = if (input$site != "Network") "fa-file-text" , color = "orange")
})
```


Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### Historic & projected network population distribution

```{r, fig.keep='none'}

renderHighchart({
  highchart() %>% 
    hc_add_series(subset(comp.pop,comp.pop$organization!="ARCH"), 
                type = "area", hcaes(x = test_date, y = pred.UNIQFRQ, 
                                                      group = organization)) %>% 
  hc_xAxis(type = "datetime", dateTimeLabelFormats = list(day = '%d of %b')) %>%
  hc_title(text = "") %>% 
  hc_subtitle(text = "") %>% 
  hc_tooltip(pointFormat = "<span style=\"color:{series.color}\">{series.name}</span>:
             <b>{point.percentage:.1f}%</b> ({point.y:,.0f} patients)<br/>",
             shared = TRUE) %>%

  hc_yAxis(title = list(text = "% of total patient population")) %>% 
  hc_plotOptions(area = list(
    stacking = "percent",
    lineColor = "#ffffff",
    lineWidth = 1,
    marker = list(
      lineWidth = 1,
      lineColor = "#ffffff"
    )))
})
    
    
    
```


### Projected network/site patient population

```{r, fig.keep='none'}

renderHighchart({
  if (input$site == "Network"){
   highchart() %>% 
  hc_add_series(subset(comp.pop,comp.pop$organization=="NETWORKNAME"), 
                  type = "arearange", hcaes(x = test_date, low = round(pred.low.UNIQFRQ,0), 
                                                  high= round(pred.high.UNIQFRQ,0)),color="gray",fillOpacity=1,showInLegend = FALSE) %>% #enableMouseTracking = FALSE
    hc_add_series(subset(comp.pop,comp.pop$organization=="ARCH"),
                  type = "line", hcaes(x = test_date, y = round(pred.UNIQFRQ,0)),fillOpacity=0.1,showInLegend = FALSE) %>%
  hc_add_series(subset(comp.pop,comp.pop$organization=="ARCH"), 
                type = "point", hcaes(x = test_date, y = round(pred.UNIQFRQ,0), color= projection),showInLegend = FALSE,enableMouseTracking = FALSE) %>%
    hc_xAxis(type = "datetime", dateTimeLabelFormats = list(day = '%d of %b')) %>% 
    hc_tooltip(pointFormat = "",
               shared = TRUE) %>%
    hc_title(text = "Estimated Network Patient Population") %>% 
    hc_subtitle(text = "Source: DQe-c runs") %>% 
    hc_plotOptions(line = list(
      dataLabels = list(enabled = TRUE),
      enableMouseTracking = FALSE)
    )
  } else if (input$site != "Network"){
    highchart() %>% 
  hc_add_series(subset(comp.pop,comp.pop$organization==input$site),
                type = "line", hcaes(x = test_date, y = round(pred.UNIQFRQ,0)),fillOpacity=0.1,showInLegend = FALSE) %>%
  # hc_add_series(subset(comp.pop,comp.pop$organization==input$site), 
  #                 type = "arearange", hcaes(x = test_date, low = round(pred.low.UNIQFRQ,0), 
  #                                                 high= round(pred.high.UNIQFRQ,0)),color="gray",fillOpacity=0.05,showInLegend = FALSE) %>% #enableMouseTracking = FALSE

  hc_add_series(subset(comp.pop,comp.pop$organization==input$site), 
                type = "point", hcaes(x = test_date, y = round(pred.UNIQFRQ,0), color= projection),showInLegend = FALSE,enableMouseTracking = FALSE) %>%
    hc_xAxis(type = "datetime", dateTimeLabelFormats = list(day = '%d of %b')) %>% 
    hc_tooltip(pointFormat = "",
               shared = TRUE) %>%
    hc_title(text = "") %>% 
    hc_subtitle(text = "") %>% 
    hc_plotOptions(line = list(
      dataLabels = list(enabled = TRUE),
      enableMouseTracking = FALSE)
    )
  }
})
    
    
    
```


### Table availability across network/site

```{r, fig.keep='none'}
renderHighchart({
  if (input$site == "Network"){
    
count.tables.latest = as.data.frame.matrix(table(DQ.Master.latest$organization,DQ.Master.latest$TabNam))
for (i in 1:dim(count.tables.latest)[2]){
  for (j in 1:dim(count.tables.latest)[1]) {
    count.tables.latest[j,i] = ifelse(count.tables.latest[j,i] > 0, 1,count.tables.latest[j,i])
  }
}
ratio.tables.latest = data.frame(apply(count.tables.latest,2,sum)/length(unique(DQ.Master$organization)))
ratio.tables.latest$tables = row.names(ratio.tables.latest)
row.names(ratio.tables.latest) = NULL
colnames(ratio.tables.latest) = c("rate.availability","table")
ratio.tables.latest$size = 1
ratio.tables.latest$ratio.availability = round(ratio.tables.latest$rate.availability*100,digits=0)

tm <- treemap(ratio.tables.latest,
              index = "table",
              vSize = "ratio.availability",
              vColor="rate.availability",
              type="value",
              title = "",
              title.legend = "Table availability across network",
              border.col = "white",
              position.legend = "bottom",
              range = c(0,100)
)

highchart() %>% 
  hc_add_series_treemap(tm, allowDrillToNode = TRUE,
                        layoutAlgorithm = "squarified") #%>% 
  }
else if (input$site != "Network"){
  count.tables.latest.site = as.data.frame.matrix(table(DQ.Master.latest$organization,DQ.Master.latest$TabNam))
for (i in 1:dim(count.tables.latest.site)[2]){
  for (j in 1:dim(count.tables.latest.site)[1]) {
    count.tables.latest.site[j,i] = ifelse(count.tables.latest.site[j,i] > 0, 1,count.tables.latest.site[j,i])
  }
}

count.tables.latest.site = subset(count.tables.latest.site, row.names(count.tables.latest.site) == input$site)
ratio.tables.latest.site = data.frame(apply(count.tables.latest.site,2,sum))
ratio.tables.latest.site$tables = row.names(ratio.tables.latest.site)
row.names(ratio.tables.latest.site) = NULL
count.tables.latest.site = data.frame(count.tables.latest.site)
count.tables.latest.site$organization = as.character(row.names(count.tables.latest.site))

colnames(ratio.tables.latest.site) = c("rate.availability","table")
ratio.tables.latest.site$size = 1
ratio.tables.latest.site$ratio.availability = round(ratio.tables.latest.site$rate.availability*100,digits=0)

ratio.tables.latest.site2 = reactive({ratio.tables.latest.site})
tm2 <- treemap(ratio.tables.latest.site,
        index = "table",
        vSize = "ratio.availability",
        vColor="ratio.availability",
        type="value",
        title = paste0("Table availability @ ",input$site,"." ),
        title.legend = "Table availability across network",
        border.col = "white",
        position.legend = "bottom",
        range = c(0,100)
        )

highchart() %>% 
  hc_add_series_treemap(tm2, allowDrillToNode = TRUE,
                        layoutAlgorithm = "squarified") #%>% 
  # hc_add_theme(thm)
}
})
```



Preview Changes
=======================================================================
Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### changes over time

```{r, fig.keep='none'}
renderPlot({

key.variables = subset(DQ.Master, 
       (DQ.Master$TabNam == "demographic" & DQ.Master$ColNam == "patid") | 
         (DQ.Master$TabNam == "encounter" & DQ.Master$ColNam == "encounterid") |
         (DQ.Master$TabNam == "diagnosis" & DQ.Master$ColNam == "diagnosisid") |
         (DQ.Master$TabNam == "procedures" & DQ.Master$ColNam == "proceduresid"))


options(scipen=999)

if (input$site == "Network") {
ggplot(key.variables,aes(x=test_date, y = UNIQFRQ, group=factor(organization))) +
  # geom_boxplot(aes(color=organization), alpha=0.2) +
  geom_point(aes(color=organization), shape = 21, size = 4, stroke= 1) + 
  geom_line(aes(color=organization), alpha= 0.6)+
  geom_text_repel(aes(label = organization))+
  facet_wrap( ~ TabNam, scale="free_y", ncol = 2) +
  scale_fill_gradient(limits=c(0, 1),low="#FFFAF0", high="#EE2C2C", guide=F ,na.value="white")+
  theme(panel.grid.major.x = element_line(colour = "gray"),
        axis.text.x = element_text(angle = 0, hjust = 1),
        axis.text.y = element_text(angle = 0, hjust = 1)) +
    # theme_minimal() +
    theme(legend.position="none") +
  xlab("") + ylab("")
} else if (input$site != "Network"){
  key.variables.site = subset(key.variables, key.variables$organization == input$site)
    ggplot(key.variables,aes(x=test_date, y = UNIQFRQ, group=factor(organization))) +
  # geom_boxplot(aes(color=organization), alpha=0.2) +
  geom_point(color = "white",shape = 21, size = 4, stroke= 1) + 
  geom_line(color = "white", alpha= 0.6)+
  geom_point(data = key.variables.site,
             aes(x=test_date, y = UNIQFRQ), 
             color = "red",shape = 21, size = 4, stroke= 2) + 
  geom_line(data = key.variables.site,
             aes(x=test_date, y = UNIQFRQ), 
             color = "red", alpha= 0.6)+
  # geom_text_repel(data = key.variables.site, 
  #                 aes(label = organization))+
  facet_wrap( ~ TabNam, scale="free_y", ncol = 2) +
  scale_fill_gradient(limits=c(0, 1),low="#FFFAF0", high="#EE2C2C", guide=F ,na.value="white")+
  theme(panel.grid.major.x = element_line(colour = "gray"),
        axis.text.x = element_text(angle = 0, hjust = 1),
        axis.text.y = element_text(angle = 0, hjust = 1)) +
    # theme_minimal() +
    theme(legend.position="none") +
  xlab("") + ylab("")
}

})
```


Missingness 
=======================================================================
Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### missingness in available tables

```{r, fig.keep='none'}
renderPlot({

DQ.Master.latest.nonraw = subset(DQ.Master.latest,  DQ.Master.latest$DQLVL %in% c("H","X") )
DQ.Master.latest.nonraw.aggregate1 = DQ.Master.latest.nonraw  %>% 
  group_by(TabNam,organization) %>% 
  summarise(FRQ = mean(FRQ),
            # frq2 = sum(FRQ),
            numb = length(TabNam),
            MS1_FRQ = sum(MS1_FRQ),
            MS2_FRQ = sum(MS2_FRQ))

DQ.Master.latest.nonraw.aggregate1$FRQ = DQ.Master.latest.nonraw.aggregate1$FRQ * DQ.Master.latest.nonraw.aggregate1$numb

DQ.Master.latest.nonraw.aggregate1$MSs_PERC = (round((DQ.Master.latest.nonraw.aggregate1$MS1_FRQ+DQ.Master.latest.nonraw.aggregate1$MS2_FRQ)/DQ.Master.latest.nonraw.aggregate1$FRQ,2))
DQ.Master.latest.nonraw.aggregate1$numb = NULL
DQ.Master.latest.nonraw.aggregate1 = data.frame(DQ.Master.latest.nonraw.aggregate1)
DQ.Master.latest.nonraw.aggregate1$perc = percent(DQ.Master.latest.nonraw.aggregate1$MSs_PERC)


aggregate2x = DQ.Master.latest.nonraw.aggregate1  %>% 
  group_by(TabNam) %>% 
  summarise(FRQ = sum(FRQ),
            # numb = length(TabNam),
            MS1_FRQ = sum(MS1_FRQ),
            MS2_FRQ = sum(MS2_FRQ))

aggregate2x$MSs_PERC = (round((aggregate2x$MS1_FRQ+aggregate2x$MS2_FRQ)/aggregate2x$FRQ,4))
aggregate2x$organization = "Network"
aggregate2x = data.frame(select(aggregate2x,TabNam,organization,FRQ,MS1_FRQ,MS2_FRQ,MSs_PERC))
aggregate2x$perc = percent(aggregate2x$MSs_PERC)

# table.site.aggregated.missingness 
tab.sit.agg.miss = rbind(DQ.Master.latest.nonraw.aggregate1, aggregate2x)

if (input$site == "Network") {
  ggplot(aggregate2x, aes(x=MSs_PERC,y=reorder(TabNam,-MSs_PERC),label = perc)) +
  geom_point(aes(fill = MSs_PERC),shape = 21, colour = "black",  size = 8, stroke = 3, alpha = 0.9) +
  geom_point(data=DQ.Master.latest.nonraw.aggregate1, aes(x=MSs_PERC,y=reorder(TabNam,-MSs_PERC)),
             shape = 21, colour = "black",  size = 4, stroke = 3, alpha = 0.3) +
  geom_text(vjust = 3, hjust = .5, nudge_y = 0, size = 4)+

  scale_fill_gradient2(limits=c(0, 1),low="#FFFAF0", high="#EE2C2C", guide=F,na.value="white")+
  # theme_grey(base_size = base_size) +
  labs(x = "", y = "") +
  scale_x_continuous(limits = c(0, 1)) +
      scale_y_discrete(limits=c("death","demographic","diagnosis","encounter",
                            "enrollment","harvest","lab_result_cm","prescribing",
                            "vital","procedures","condition","dispensing")) +
  theme_minimal() +
  theme(panel.grid.major.y = element_line(color = "gray",size = 2.5),
        panel.grid.major.x = element_line(colour = "black", linetype = "dotted"),
        axis.text.y=element_text(size=20, face="bold"))
} else if (input$site != "Network") {
  DQ.Master.latest.nonraw.aggregate1.site = subset(DQ.Master.latest.nonraw.aggregate1,
                                                   DQ.Master.latest.nonraw.aggregate1$organization == input$site)
  
  aggregate2x = subset(DQ.Master.latest.nonraw.aggregate1,DQ.Master.latest.nonraw.aggregate1$organization != input$site )  %>% 
  group_by(TabNam) %>% 
  summarise(FRQ = sum(FRQ),
            # numb = length(TabNam),
            MS1_FRQ = sum(MS1_FRQ),
            MS2_FRQ = sum(MS2_FRQ))

aggregate2x$MSs_PERC = (round((aggregate2x$MS1_FRQ+aggregate2x$MS2_FRQ)/aggregate2x$FRQ,4))
aggregate2x$organization = "Network"
aggregate2x = data.frame(select(aggregate2x,TabNam,organization,FRQ,MS1_FRQ,MS2_FRQ,MSs_PERC))
aggregate2x$perc = percent(aggregate2x$MSs_PERC)


  ggplot(aggregate2x, aes(x=MSs_PERC,y=TabNam,label = perc)) +
  geom_point(aes(fill = NULL),shape = 21, colour = "black",  size = 8, stroke = 3, alpha = 0.9) +
      scale_fill_gradient2(limits=c(0, 1),low="#FFFAF0", high="#EE2C2C", guide=F,na.value="white")+
  geom_point(data=DQ.Master.latest.nonraw.aggregate1, aes(x=MSs_PERC,y=TabNam),
             shape = 21, colour = "black",  size = 4, stroke = 3, alpha = 0.3) +
      # geom_text(vjust = 3, hjust = .5, nudge_y = 0, size = 4)+
    geom_point(data=DQ.Master.latest.nonraw.aggregate1.site, aes(x=MSs_PERC,y=TabNam),
             shape = 73, colour = "red",  size = 12, alpha = 1) +
          geom_text(data=DQ.Master.latest.nonraw.aggregate1.site,vjust = 3, hjust = .5, nudge_y = 0, size = 4)+

  # theme_grey(base_size = base_size) +
  labs(x = "", y = "") +
  scale_x_continuous(limits = c(0, 1)) +
  scale_y_discrete(limits=c("death","demographic","diagnosis","encounter",
                            "enrollment","harvest","lab_result_cm","prescribing",
                            "vital","procedures","condition","dispensing")) +
  theme_minimal() +
  theme(panel.grid.major.y = element_line(color = "gray",size = 2.5),
        panel.grid.major.x = element_line(colour = "black", linetype = "dotted"),
        axis.text.y=element_text(size=20, face="bold"))
}

})
```

### changes in missingness in available tables

```{r, fig.keep='none'}
renderPlot({

#subseting to non-raw columns only
DQ.Master.all.nonraw = subset(DQ.Master,  DQ.Master$DQLVL %in% c("H","X") )

DQ.Master.all.nonraw.aggregate = DQ.Master.all.nonraw  %>% 
  group_by(TabNam,organization,test_date) %>% 
  summarise(FRQ = mean(FRQ),
            numb = length(TabNam),
            MS1_FRQ = sum(MS1_FRQ),
            MS2_FRQ = sum(MS2_FRQ))

DQ.Master.all.nonraw.aggregate$FRQ = DQ.Master.all.nonraw.aggregate$FRQ * DQ.Master.all.nonraw.aggregate$numb

DQ.Master.all.nonraw.aggregate$MSs_PERC = (round((DQ.Master.all.nonraw.aggregate$MS1_FRQ+DQ.Master.all.nonraw.aggregate$MS2_FRQ)/
                                                   DQ.Master.all.nonraw.aggregate$FRQ,2))
DQ.Master.all.nonraw.aggregate$numb = NULL
DQ.Master.all.nonraw.aggregate = data.frame(DQ.Master.all.nonraw.aggregate)
DQ.Master.all.nonraw.aggregate$perc = percent(DQ.Master.all.nonraw.aggregate$MSs_PERC,digits = 0)

if (input$site == "Network") {
ggplot(DQ.Master.all.nonraw.aggregate,aes(x=test_date, y = MSs_PERC, group=factor(organization)))+
  # geom_boxplot(aes(color=organization), alpha=0.2) +
  geom_point(aes(color=organization), shape = 21, size = 4, stroke= 1, guide=F) + 
  geom_line(aes(color=organization), alpha= 0.6, guide=F)+
  # geom_text_repel(aes(label = organization),vjust = 3, hjust = .5, nudge_y = 0, size = 4)+
  # geom_text_repel(aes(label = perc),vjust = 3, hjust = .5, nudge_y = 0, size = 4)+
  facet_wrap( ~ TabNam, scale="free_y", ncol = 4) +
  scale_fill_gradient(limits=c(0, 1),low="#FFFAF0", high="#EE2C2C", guide=F ,na.value="white")+
  theme(panel.grid.major.x = element_line(colour = "gray"),
        axis.text.x = element_text(angle = 0, hjust = 1),
        axis.text.y = element_text(angle = 0, hjust = 1)) +
    # theme_minimal() +
    theme(legend.position="bottom") + guides(colour = guide_legend(nrow = 1)) +
  xlab("") + ylab("") #+ coord_polar(theta = "x", direction=1 )

} else if (input$site != "Network") {

DQ.Master.all.nonraw.aggregate$site2 = ifelse(DQ.Master.all.nonraw.aggregate$organization == input$site, 1, 0)

ggplot(DQ.Master.all.nonraw.aggregate,aes(x=test_date, y = MSs_PERC, group=factor(organization))) +
  # geom_boxplot(aes(color=organization), alpha=0.2) +
  geom_point(aes(color = factor(site2)), shape = 21, size = 4, stroke= 3, guide=F,alpha= 0.6) + 
  geom_line(aes(color = factor(site2)), alpha= 0.6, guide=F) +
  # geom_text_repel(aes(label = organization),vjust = 3, hjust = .5, nudge_y = 0, size = 4)+
  geom_text_repel(data=subset(DQ.Master.all.nonraw.aggregate, DQ.Master.all.nonraw.aggregate$organization == input$site),aes(label = perc),vjust = 3, hjust = .5, nudge_y = 0, size = 4)+
  facet_wrap( ~ TabNam, scale="free_y", ncol = 4) +
  scale_colour_manual(values = c("white","red"),
                    labels = c("other sites",paste0(input$site)))+
theme(panel.grid.major.x = element_line(colour = "gray"),
        axis.text.x = element_text(angle = 0, hjust = 1),
        axis.text.y = element_text(angle = 0, hjust = 1)) +
    # theme_minimal() +
    theme(legend.position="bottom") + guides(colour = guide_legend(nrow = 1)) +
  xlab("") + ylab("")
}

})
```


Missingness (by column) **beta**
=======================================================================
```{r, include=FALSE}
DQ.Master.latest.aggregate2 <- DQ.Master.latest  %>% 
  group_by(TabNam,ColNam) %>% 
  summarise(FRQ = sum(FRQ),UNIQFRQ = sum(UNIQFRQ),MS1_FRQ = sum(MS1_FRQ),MS2_FRQ = sum(MS2_FRQ))

DQ.Master.latest.aggregate2$MSs_PERC = (round((DQ.Master.latest.aggregate2$MS1_FRQ+
                                                 DQ.Master.latest.aggregate2$MS2_FRQ)/DQ.Master.latest.aggregate2$FRQ,2))


DQ.Master.latest.aggregate2$test_date = as.character(format(Sys.Date(),"%m-%d-%Y"))
DQ.Master.latest.aggregate2$organization = Net.Name
DQ.Master.latest.aggregate2$round = 1
DQ.Master.latest.aggregate2$perc = percent(DQ.Master.latest.aggregate2$MSs_PERC)

# 
DQ.Master.latest$perc = percent(DQ.Master.latest$MSs_PERC)
##############
##############
###############


```


Row {.tabset .tabset-fade vertical_layout: fill}
-----------------------------------------------------------------------

### completeness by table/column treemap (*beta*) 

```{r, fig.keep='none'}
renderHighchart({
  
  if (names(dev.cur()) != "null device") dev.off()
pdf(NULL)

if (input$site == "Network") {
#   d = DQ.Master.latest.aggregate2 %>%
#   group_by(TabNam) %>%
#   summarise(MS = sum(as.numeric(FRQ)))
# 
# DQ.Master.latest.aggregate2 = merge(DQ.Master.latest.aggregate2,d, by= "TabNam", all.x = TRUE)
# DQ.Master.latest.aggregate2$MS = log10(DQ.Master.latest.aggregate2$MS)
DQ.Master.latest.aggregate2$MS = log10(as.numeric(DQ.Master.latest.aggregate2$FRQ))

  tm3 = treemap(DQ.Master.latest.aggregate2,
        index = c("ColNam"),
        vSize = "MS",
        vColor="MSs_PERC",
        type="value",
        title = "",
        # title.legend = "column availability across network",
        border.col = "white",
        position.legend = "bottom",
        palette = rev(viridis(6)),
        range = c(0,100)
)
  
  highchart() %>% 
    hc_add_series_treemap(tm3, allowDrillToNode = TRUE,
                          layoutAlgorithm = "squarified") #%>% 
    # hc_add_theme(thm)
} else if (input$site != "Network") {
  
  dato = subset(DQ.Master.latest, DQ.Master.latest$organization == input$site)
  dato$MS = log10(as.numeric(dato$FRQ))

  tm3 = treemap(dato,
        index = c("ColNam"),
        vSize = "MS",
        vColor="MSs_PERC",
        type="value",
        title = "",
        # title.legend = "column availability across network",
        border.col = "white",
        position.legend = "bottom",
        palette = rev(viridis(6)),
        range = c(0,100)
)
  
  highchart() %>% 
    hc_add_series_treemap(tm3, allowDrillToNode = TRUE,
                          layoutAlgorithm = "squarified") #%>% 
    # hc_add_theme(thm)

  
  }
  
  
  
  
})

```

### missingness by column **collapsible tree** (*beta*)

```{r, fig.keep='last'}
renderCollapsibleTree({
if (input$site == "Network") {
  DQ.Master.latest.aggregate2 %>%
  group_by(TabNam, ColNam) %>%
  summarise(MS = (sum(sum(as.numeric(MS1_FRQ))+sum(as.numeric(MS2_FRQ))))/sum(as.numeric(FRQ))
  ) %>%
  collapsibleTreeSummary(
    hierarchy = c("TabNam", "ColNam"),
    root = paste0(unique(DQ.Master.latest.aggregate2$organization)),
    width = 800,
    attribute = "MS",
    maxPercent = 75
  )
} else if (input$site != "Network") {
  
  dat = subset(DQ.Master.latest, DQ.Master.latest$organization == input$site)
  root = as.character(unique(dat$organization))
  dat <- dat %>%
  group_by(TabNam, ColNam) %>%
  summarise(MS = (sum(sum(as.numeric(MS1_FRQ))+sum(as.numeric(MS2_FRQ))))/sum(as.numeric(FRQ))
  ) 
  dat$MS <- ifelse(dat$MS == 0, 0.000001,dat$MS)
  
  dat %>%
  collapsibleTreeSummary(
    hierarchy = c("TabNam", "ColNam"),
    root = paste0(root),
    width = 800,
    attribute = "MS",
    maxPercent = 75
  )
  
}

})
```


Missingness (key indicators) 
=======================================================================
Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### missingness in key indicators

```{r, fig.keep='none'}
renderPlot({

if (input$site == "Network") {
ggplot(withouts.network.latest.aggregate, aes(x=missing.ratio,y=group,
                                              label = perc)) +
  geom_point(aes(fill = missing.ratio),shape = 21, colour = "black",  size = 8, stroke = 3, alpha = 0.9) +
  geom_point(data=withouts.network.latest, aes(x=missing.ratio,y=group),
             shape = 21, colour = "black",  size = 4, stroke = 3, alpha = 0.3) +
  geom_text(vjust = 3, hjust = .5, nudge_y = 0, size = 4)+

  scale_fill_gradient(limits=c(0, 1),low="#FFFAF0", high="#EE2C2C", guide=F,na.value="white")+
  # theme_grey(base_size = base_size) +
  labs(x = "", y = "") +
  scale_x_continuous(limits = c(0, 1)) +
  scale_y_discrete(limits=c("blood_pressure","ethnicity","gender","height","race","smoking","weight")) +
  theme_minimal() +
  theme(panel.grid.major.y = element_line(color = "gray",size = 2.5),
        panel.grid.major.x = element_line(colour = "black", linetype = "dotted"),
        axis.text.y=element_text(size=20, face="bold"))
} else if (input$site != "Network") {
  
  withouts.network.latest.site = subset(withouts.network.latest, withouts.network.latest$organization == input$site)
  
  withouts.network.latest.aggregate <- subset(withouts.network.latest, withouts.network.latest$organization != input$site) %>% group_by(group) %>% summarise(missing.pop = sum(missing.population),denominator = sum(denominator))

# 
withouts.network.latest.aggregate$missing.ratio <- round((withouts.network.latest.aggregate$missing.pop/withouts.network.latest.aggregate$denominator),4)
withouts.network.latest.aggregate$perc <- percent(withouts.network.latest.aggregate$missing.ratio)
withouts.network.latest.aggregate$organization <- "Network"
withouts.network.latest.aggregate$test_date <- as.character(format(Sys.Date(),"%m-%d-%Y"))


  ggplot(withouts.network.latest.aggregate, aes(x=missing.ratio,y=group,
                                              label = perc)) +
  geom_point(aes(fill = NULL),shape = 21, colour = "black",  size = 8, stroke = 3, alpha = 0.8) +
  geom_point(data=withouts.network.latest, aes(x=missing.ratio,y=group),
             shape = 21, colour = "black",  size = 4, stroke = 3, alpha = 0.3) +
  scale_fill_gradient(limits=c(0, 1),low="#FFFAF0", high="#EE2C2C", guide=F,na.value="white")+
   geom_point(data=withouts.network.latest.site, aes(x=missing.ratio,y=group),
             shape = 73, colour = "red",  size = 12, alpha = 0.9) +
    geom_text_repel(data=withouts.network.latest.site,aes(label = perc),
                  nudge_y = 0, size = 4, box.padding = 0.5, point.padding = 0.5)+
  # theme_grey(base_size = base_size) +
  labs(x = "", y = "") +
  scale_x_continuous(limits = c(0, 1)) +
  scale_y_discrete(limits=c("blood_pressure","ethnicity","gender","height","race","smoking","weight")) +
  theme_minimal() +
  theme(panel.grid.major.y = element_line(color = "gray",size = 2.5),
        panel.grid.major.x = element_line(colour = "black", linetype = "dotted"),
        axis.text.y=element_text(size=20, face="bold"))
  
}
  
})
```

### changes in missingness in key indicators

```{r, fig.keep='none'}
renderPlot({
if (input$site == "Network") {
ggplot(withouts.network,aes(x=test_date, y = missing.percentage, group=factor(organization)))+
  # geom_boxplot(aes(color=organization), alpha=0.2) +
  geom_point(aes(color=organization), shape = 21, size = 4, stroke= 1, guide=F) + 
  geom_line(aes(color=organization), alpha= 0.6, guide=F)+
  # geom_text_repel(aes(label = organization),vjust = 3, hjust = .5, nudge_y = 0, size = 4)+
  # geom_text_repel(aes(label = perc),vjust = 3, hjust = .5, nudge_y = 0, size = 4)+
  facet_wrap( ~ group, scale="free_y", ncol = 5) +
  scale_fill_gradient(limits=c(0, 1),low="#FFFAF0", high="#EE2C2C", guide=F ,na.value="white")+
  theme(panel.grid.major.x = element_line(colour = "gray"),
        axis.text.x = element_text(angle = 0, hjust = 1),
        axis.text.y = element_text(angle = 0, hjust = 1)) +
    # theme_minimal() +
    theme(legend.position="bottom") + guides(colour = guide_legend(nrow = 1)) +
  xlab("") + ylab("") #+ coord_polar(theta = "x", direction=1 )
} else if (input$site != "Network") {
  
  withouts.network$site2 = ifelse(withouts.network$organization == input$site, 1, 0)
  
  ggplot(withouts.network,aes(x=test_date, y = missing.percentage, group=factor(organization)))+
  # geom_boxplot(aes(color=organization), alpha=0.2) +
  geom_point(aes(color = factor(site2)), shape = 21, size = 4, stroke= 3, guide=F) + 
  geom_line(aes(color = factor(site2)), alpha= 0.6, guide=F)+
  # geom_text_repel(aes(label = organization),vjust = 3, hjust = .5, nudge_y = 0, size = 4)+
  geom_text_repel(data=subset(withouts.network,withouts.network$organization == input$site),aes(label = perc),vjust = 3, hjust = .5, nudge_y = 0, size = 4)+
  facet_wrap( ~ group, scale="free_y", ncol = 5) +
  scale_colour_manual(values = c("white","red"),
                    labels = c("other sites",paste0(input$site)))+
  theme(panel.grid.major.x = element_line(colour = "gray"),
        axis.text.x = element_text(angle = 0, hjust = 1),
        axis.text.y = element_text(angle = 0, hjust = 1)) +
    # theme_minimal() +
    theme(legend.position="bottom") + guides(colour = guide_legend(nrow = 1)) +
  xlab("") + ylab("")
  
}


})
```
